---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  eval = FALSE
)
```
# ari_paper

<!-- badges: start -->
<!-- badges: end -->

The goal of ari_paper is to showcase the [`ari` package](https://cran.r-project.org/package=ari).  We show how to use each function and the output videos.  This README uses the [`video`](https://github.com/muschellij2/video) package to render videos inside the markdown.  The paper can be viewed at https://johnmuschelli.com/ari_paper/.

```{r, eval = TRUE, echo = FALSE}
library(video)
```

## Making videos with `ari`: `ari_stitch`

```{r stitch, message = FALSE}
library(tuneR)
library(ari)
result = ari_stitch(
  ari_example(c("mab1.png", "mab2.png")),
  list(noise(), noise()),
  output = "noise.mp4")
isTRUE(result)
attributes(result)$outfile
```

```{r, eval = TRUE, echo = FALSE}
video::video("noise.mp4")
```


## Creating Speech from Text: `ari_spin`

Let us take a part of Mercutio's speech from Shakespeare's Romeo and Juliet [@shakespeare2003romeo] and overlay it on 2 images from the Wikipedia page about Mercutio (https://en.wikipedia.org/wiki/Mercutio):


```{r romeo}
res = ffmpeg_audio_codecs()
fdk_enabled = grepl("fdk", res[ res$codec == "aac", "codec_name"])
if (fdk_enabled) {
  audio_codec = "libfdk_aac"
} else {
  audio_codec = "aac"
}
speech =  c(
  "I will now perform part of Mercutio's speech from Shakespeare's Romeo and Juliet.", 
  "O, then, I see Queen Mab hath been with you.
   She is the fairies' midwife, and she comes
   In shape no bigger than an agate-stone
   On the fore-finger of an alderman,
   Drawn with a team of little atomies
   Athwart men's noses as they lies asleep;")
mercutio_file = "death_of_mercutio.png"
mercutio_file2 = "mercutio_actor.png"

output = "romeo.mp4"
if (!file.exists(output)) {
  run_voice = "Joanna"
  ari_spin(
    c(mercutio_file, mercutio_file2),
    speech, output = output, voice = run_voice,
    service = "amazon",
    audio_codec = audio_codec)
}
```

```{r, eval = TRUE, echo = FALSE}
video::video("romeo.mp4")
```

We can also generate the video using the voice `Brian`, which is an British English male voice:

```{r romeo_gb, echo = FALSE, eval = TRUE}
output = "romeo_gb.mp4"
if (!file.exists(output)) {
  run_voice = "Brian"
  ari_spin(
    c(mercutio_file, mercutio_file2),
    speech, output = output, voice =  run_voice,
    service = "amazon",
    audio_codec = audio_codec)
}
```

```{r, eval = TRUE, echo = FALSE}
video::video("romeo_gb.mp4")
```
